Secure Composition of Robust and Optimising Compilers

### 2023-09-25 csf/main.tex
Add note

\textbf{Triviality.} Note that the theorem may give trivial results, i.e., the intersection of classes $\class[_1]$ and $\class[_2]$ may be empty. 
For example, consider $\rtp{\cc{\src{L}}{\trg{L}}}{\tmssafe}$ and $\rtp{\cc{\trg{L}}{\obj{L}}}{\smssafe}$, where $\cc{\trg{L}}{\obj{L}}$ introduces code that allocates a table that stores bounds information of pointers, but fails to insert code that deallocates this table.
By \Cref{def:trace:tmsdef}, this violates $\tmssafe$.
Therefore, no behavior resulting from programs produced by the $\cc{\trg{L}}{\obj{L}}$ compiler is secure with respect to $\tmssafe$, but only for $\smssafe$.
In turn, % TODO TODO TODO FIXME

>>>>

Note that the theorem may not be applicable in certain cases.
For example, consider $\rtp{\cc{\src{L}}{\trg{L}}}{\tmssafe}$ and $\rtp{\cc{\trg{L}}{\obj{L}}}{\smssafe}$, where $\cc{\trg{L}}{\obj{L}}$ introduces code that allocates a table that stores bounds information of pointers, but fails to insert code that deallocates this table.
By \Cref{def:trace:tmsdef}, this violates $\tmssafe$.
Therefore, no behavior resulting from programs produced by the $\cc{\trg{L}}{\obj{L}}$ compiler is secure with respect to $\tmssafe$, but only for $\smssafe$.
This, however, is a requirement of the preservation statement (the property of interest must be in $\class[_1]\cap\class[_2]$).
